Proportional multi-state multiple-cohort life table model

### 2018-04-19 MSLT/MSLTdoc.Rmd
Deleted () from ylds variable

5) Change all uper cases to lower case
```{r, echo=TRUE}
GBDdata <- mutate_all(GBDdata, funs(tolower))
```

>>>>

5) Change all uper cases to lower case and delete () from variables. 
```{r, echo=TRUE}
GBDdata <- mutate_all(GBDdata, funs(tolower))
GBDdata$measure[GBDdata$measure=="ylds (years lived with disability)"] <- "ylds"
```
